### 2020-02-06 thesis_template/2_RelatedWork/relatedWork.tex
added description
resolved
added

@@

Comparing operation on various smart pointer type. 
Rc<T> enables value to have multiple owners, but the value should be immutable. Rx<T> is used in case of single thread. 
When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Arc<T>. 
When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable
of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
That is why RefCell<T> is expensive so that the state of mutable consistency should tracked. 
As Cell<T>, the value is copied in and out of the Cell<T> instead of getting refrence to it. 
In addition, Mutex<T> provides intetior mutability across multi-thread.

>>>>

\section{Possible Graph Structure in Rust}
\label{sec:history}
In Rust, there are two essential problems to construct graph structure, lifetime and mutability.

The first problem is about what kind of pointer to use to point to other nodes. 
Since graph can be cyclic, so the ownership consept in Rust is violated if we use Box<Node>.

All of graph structure are immutable at least at creation time. Because graph may have cyclic, 
we can not create graph at one statement. Although edge of graph has to be mutable to create entire graph structure, 
we might need multiple references to edges, which violates basic rule of Rust programming.

One solution is to use raw pointers. This is the most flexible approach, but also the most dangerous. 
By taking this way, we are ignoring all the benefits of Rust.

For

@@

Comparing operation on various smart pointer type. 
Rc<T> enables value to have multiple owners, but the value should be immutable. Rc<T> is used in case of single thread. 
When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Rc<T>. 
When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable
of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
That is why RefCell<T> is expensive so that the state of mutable consistency should tracked. 
As Cell<T>, the value is copied in and out of the Cell<T> instead of getting refrence to it. 
In addition, Mutex<T> provides intetior mutability across multi-thread.
